\begin{recipe}
[%
  portion = {\portion{4}}
]
{Chicken Fricass\'{e}e}
  \ingredients[17]{%
    \unit[2]{lb}                  & chicken breast (About 4 breasts) \\
    to taste                      & salt \\
    to taste                      & ground black pepper \\
    \unit[1]{Tbsp}                & butter \\
    \unit[1]{Tbsp}                & bacon fat or olive oil \\
    \unit[1]{lb}                  & sliced cremini mushrooms \\
    1                             & chopped medium onion \\
    \unit[\nicefrac{1}{4}]{cup}   & dry white wine \\
    \unit[1]{Tbsp}                & flour \\
    \unit[4]{cloves}              & garlic (minced) \\
    \unit[1\nicefrac{1}{2}]{cups} & chicken broth \\
    \unit[\nicefrac{1}{3}]{cup}   & sour cream \\
    1                             & egg yolk \\
    \unit[2]{tsp}                 & lemon juice \\
    \unit[2]{tsp}                 & tarragon (minced) \\
    \unit[\nicefrac{1}{2}]{tsp}   & ground nutmeg
  }
  \preparation{%
    \step Pat the chicken dry with paper towels.
    \step Season chicken with salt and black pepper.
    \step Heat the butter and bacon fat or oil in a stainless steel skillet over medium-high heat.
    \step Place chicken pieces in the skillet and cook until brown (about \unit[4]{mins})
    \step Using tongs, flip the chicken abd cook until browned on the second
          side (about \unit[4]{mins} more).
    \step Transfer chicken to a large plate and cover with foil.
    \step Add the mushrooms, onion, and wine to the skillet. Cook, stirring occasionally,
          until the liquid has evaporated and the mushrooms are browned.
    \step Sprinkle the flour over the vegetables. Cook, stirring constantly, for \unit[2]{mins}.
    \step Deglaze the pan with the broth, scraping the browned bits from the bottom of the pan.
    \step Bring the mixture to a boil, then add the chicken and any accumulated
          juices to the skillet.
    \step Reduce to simmer, cover, and cook until the breasts are \unit[160-165]{\degree F}
    \step Transfer chicken to a clean plate and tent with foil.
    \step Whisk sour crean and egg yolk together in a medium bowl.
    \step Whisking constantly, slowly stir \unit[\nicefrac{1}{2}]{cups} of the souce
          from the skillet into the sour cream mixture to temper.
    \step Stirring constantly, slowly pour the sour cream mixture into the simmering sauce.
    \step Stir in the lemon juice, tarragon, and nutmeg. Return to a simmer.
    \step Season with salt and pepper to taste.
    \step Pour the sauce over the chicken and serve.
  }
\end{recipe}
%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "../master"
%%% End: 
