\begin{recipe}
[%
  portion = {\portion{4}}
]
{Ribeye With Red Wine Reduction}
\ingredients[16]{%
    2                           & \unit[1]{lb} thick-cut ribeye steaks \\
    to taste                    & salt \\
    to taste                    & ground black pepper \\
    \unit[1]{Tbsp}              & oil \\
    \unit[1]{Cup}               & red wine \\
    2                           & minced medium shallot (keep separate) \\
    2                           & white mushrooms (finely chopped) \\
    1                           & small carrot (finely chopped) \\
    1                           & bay leaf \\
    3                           & sprigs parsley \\
    \unit[\nicefrac{1}{2}]{Cup} & chicken broth \\
    \unit[\nicefrac{1}{2}]{Cup} & beef broth \\
    \unit[3]{Tbsp}              & cold butter \\
    \unit[\nicefrac{1}{2}]{tsp} & thyme leaves
  }
  \preparation{%
    \step Heat the wine, one shallot, mushrooms, carrot, bay leaf, and parsley in a
          12-inch stainless steel skillet. Cook, without simmering, until the entire
          mixture reduces by half.
    \step Strain through a fine mesh strainer and return the liquid to the clean skillet
    \step Continue to cook over low heat, without simmering, until the liquid is reduced
          to \unit[2]{Tbsp} (\unit[15-20]{mins}). Transfer the reduction to a bowl and
          wipe the skillet clean with a paper towl when reduced. (Go on with the recipe
          while this is ongoing)
    \step While the wine is reducing, heat the oven to \unit[275]{\degree F}.
    \step Pat the steaks dry with paper towels. Cut each steak in half vertically
          to create 4 \unit[8]{oz} steaks.
    \step Season the steaks liberally with salt and pepper.
    \step Place the steaks on a baking sheet, transfer to the preheated oven for 20-25
          minutes
    \step Heat the oil in the skillet over high heat. Just as the oil begins to smoke,
          place the steaks in the skillet ans sear until well browned and crusty.
    \step Using tongs, turn the steaks and cooks until well browned on the second side.
    \step Use tongs to stand the steaks on their sides to sear the edges.
    \step Transfer steaks to plate and tent with foil.
    \step Add the remaining shallot to the skillet and cook over medium-low heat until
          softened.
    \step Turn the heat to high, add the chicken and beef broths. Bring to a boil,
          scraping up the browned bits on the pan with a wooden spoon, until the liquid
          is reduced to 2 tablespoons.
    \step Turn the heat to medium-low, gently whisk in the reserved wine reduction and
          any accumulated juices from the steak plate.
    \step Whisk in the butter, one piece at a time, until melted and the sauce is
          thickened and glossy.
    \step Add the thyme and season with salt and pepper to taste.
    \step spoon over the steaks and serve immediately.
  }
\end{recipe}
%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "../master"
%%% End: 
