\documentclass[11pt, letterpaper]{article}

\input{preamble}

\begin{document}
  \begin{recipe}
  [%
    portion = {\portion{5-6}}
  ]
  {Boeuf Bourguignon}
    \ingredients[14]{%
      \unit[3]{lb}                & chuck roast \\
                                  & salt \\
                                  & pepper \\
      \unit[8]{slices}            & bacon \\
                                  & cooking oil \\
      1                           & onion (sliced) \\
      5                           & carrots (chopped) \\
      \unit[3]{cups}              & Burgundy wine \\
      \unit[\nicefrac{1}{4}]{cup} & all-purpose flour \\
      \unit[4]{cups}              & Beef stock \\
      \unit[3]{cloves}            & garlic (minced) \\
      \unit[4]{tsp}               & thyme (chopped) \\
      1                           & bay leaf \\
      \unit[2]{Tbsp}              & tomato paste \\
      \unit[1]{lb}                & pearl onions \\
      \unit[8]{oz}                & crimini mushrooms \\
      \unit[2]{Tbsp}              & butter \\
      to garnish                  & fresh parsley
    }
    \preparation{%
      \step Preheat oven to \unit[400]{\degree F}.
      \step Cut the meat into \unit[2-3]{in} chunks and season with salt and pepper.
      \step Chop bacon and fry in saut\'{e} pan until crispy, then remove.
      \step Sear beef in saute pan on all sides, then remove from the pan.
            Be careful not to overcrowd the pan. Work in batches if necessary.
      \step Add sliced onion and carrots to the pan. Saut\'{e} until softened, then remove.
      \step Deglaze with \unit[3]{cups} Burgundy wine.
      \step Place beef in Dutch oven, toss with \unit[\nicefrac{1}{4}]{cup} of all-purpose
            flour. Place uncovered in the \unit[400]{\degree F} oven for \unit[10]{mins}.
            Toss, then return to oven for an additional \unit[10]{mins}.
      \step Add vegetables, bacon, wine, and enough beef stock to just cover beef and
            vegetables. Add garlic, \unit[1]{Tbsp} of the thyme, bay leaf, and tomato paste.
            Stir to incorporate everything together.
      \step Partially cover with Dutch oven lid, reduce oven temp to \unit[325]{\degree F},
            and braise for \unit[3]{hours}, stirring occasionally.
      \step Place onions in a bowl, cover with boiling water to make them easier to peel,
            then peel them.
      \step Fry in a little bit of oil until brown. Deglaze with about \unit[1]{cup} of beef
            stock. Cover and braise for about \unit[45]{mins} or until completely soft but
            retianing their shape.
      \step Wash and chop mushrooms into quarters or halves depending on their size. Saut\'{e}
            in butter. Season with salt, pepper, and about \unit[1]{tsp} chopped thyme while
            saut\'{e}ing.
      \step After about \unit[3-3\nicefrac{1}{2}]{hours}, pull beef out of the oven, remove from
            Dutch oven, and then strain the liquid into a large saucepan. Reduce until the sauce
            is thick enough to coat the back of a spoon.
      \step Serve by plating some beef and carrots, topping with strained onions and bacon,
            pearl onions, and mushrooms. Drizzle some sauce over the pile and top with some
            freshly chopped parsley.
    }
  \end{recipe}
\end{document}